ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-08-29 reports/esi.tex
nearly at the sending to people stage

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
Karen J. Edler,\textit{$^{a}$}$^{\ast}$ Stephen C. Parker,\textit{$^{a}$} Andrew J. Jackson,\textit{$^{cd}$} \\
Richard A. Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$ \\
 \\
\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
\textit{Down, Bath, BA2 7AY, UK.} \\
\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
\textit{UK.} \\
\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
\textit{SE-211 00 Lund, Sweden.} \\
\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
\textit{Grenoble, France.} \\
\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
\textit{Manchester, Manchester, M13 9PT, UK.} \\
\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
\textit{Oxford, Didcot OX11 0QX, UK.} \\
\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
\textit{University, SE-211 00 Lund, Sweden}}
\title{ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\date{}
\begin{document}

\maketitle
\section{Probability distribution functions}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{siunitx}
\author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
Karen J. Edler,\textit{$^{a}$}$^{\ast}$ Stephen C. Parker,\textit{$^{a}$} Andrew J. Jackson,\textit{$^{cd}$} \\
Richard A. Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$ \\
 \\
\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
\textit{Down, Bath, BA2 7AY, UK.} \\
\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
\textit{UK.} \\
\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
\textit{SE-211 00 Lund, Sweden.} \\
\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
\textit{Grenoble, France.} \\
\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
\textit{Manchester, Manchester, M13 9PT, UK.} \\
\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
\textit{Oxford, Didcot OX11 0QX, UK.} \\
\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
\textit{University, SE-211 00 Lund, Sweden}}
\title{ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\date{}
\begin{document}

\maketitle
\section{Grazing incident X-ray diffraction (GIXD)}
GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figures \ref{fig:dppcgixd}-\ref{fig:dmpcgixd7}. All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough. However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid phase at all surface pressures measured. 
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/206041}
	\caption{The GIXD pattern for DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:dppcgixd}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/206151}
	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:dmpcgixd}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/206161}
	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}, the axes at in units of \si{\per\angstrom}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:dmpcgixd7}
\end{figure}
\section{Probability distribution functions}
